\documentclass[10pt]{article} % Default font size and paper size
\usepackage[utf8]{vietnam} % Tiếng Việt
\usepackage[vietnamese]{babel}
\usepackage{graphicx}
\usepackage[a4paper, total={5.5in, 9.5in}]{geometry}

\usepackage{hyperref} % Required for adding links	and customizing them
\usepackage{titlesec} % Used to customize the \section command

\usepackage{fancyhdr}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections
\begin{document}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead[L]{\#OpenToWork}
\fancyhead[R]{12/12/2022}

\par{\centering{\Huge\textsc{Tran Ngoc Huy}}\bigskip\par} % Your name
\par{\centering{\textsc{Full-Stack Developer (NodeJS, ReactJS, Linux)}}\bigskip\par} % Your name

\section{Personal Data}

\begin{tabular}{rl}
  \textsc{Name:} 						& Tran Ngoc Huy \\
  \textsc{Gender:}                  	& Male \\
  \textsc{Date of Birth:} 	  		& 14 October 2000 \\
  \textsc{Address:} 					& Thang Binh, Quang Nam, Viet Nam \\
  \textsc{Phone/Zalo/Telegram:} 					& +84 33 281 3077 \\
  \textsc{Email:} 					& \href{mailto:truongduchuy910@gmail.com}{truongduchuy910@gmail.com} \\
  \textsc{Skype:} 					& live:truongduchuy910 \\
  \textsc{Github:}				& @truongduchuy910 \\
  \textsc{Linkedin:}				& @truongduchuy910 \\
  \textsc{Family status:}				& Single \\
\end{tabular}



\section{Professional Summary}
Experienced full-stack developer with three years of experience in the industry. Seeking to leverage high proficiency in Database, Node.js, Nginx, VPS, React.js and CSS as a full-stack developer for freelancers.

\begin{itemize}
  \item Be proficient with React.js, Apollo Client, Typescript, Node.js, REST API, GraphQL API, MySQL, MongoDB, MSSQL, React Native, Angular, Redux, SWR, CSS,...
  \item Familiar with virtual private server
  \item Experience in OOP
  \item Understanding of software development tools, processes, and architecture
  \item Proficient understanding of code versioning tools (Git is preferred)
  \item Experience in the implementation of complex applications
  \item Experience with multi-tier or service-oriented web applications
  \item Experience with relational databases, SQL, and ORM technologies
  \item Experience with build tools: Webpack...
  \item Experience with search engines such as Elasticsearch...
  \item Experience in testing practices and tools
  \item Experience in agile software development
  \item Sense of responsibility, communication skills, and team spirit
  \item Willingness to learn and build a deep understanding
  \item Be able to work independently and under pressure
  \item English skills and Problem-solving skill
\end{itemize}

\paragraph{Expected salary: 900\$ - 1200\$} (NET)

\section{Work Experience \& Projects}

\subsection*{04/2022 - 11/2022: Full-stack developer at CabinEat, Ho Chi Minh. (6 months)}

Maintain, upgrade and develop new projects. Manage the work of external employees. Working with NestJS as OOP, NextJS with Typescript, ViteJS, PostgresSQL, Chakra UI, AngularJS, MongoDB, Redis, rabbitmq, Nginx, VPS, Jenkin, Github Actions, Simple Store, Cloudflare,...

\subsubsection*{Boxlink}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Help user create website via notion page (like super.so). \\
  \textbf{Team size} & 1 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Development, deployment, maintenance, upgrade. \\
  \textbf{Technologies used} & MongoDB, ItoaJS, NextJS, PM2, Vercel DNS, Bootstrap, \\
                             & Github actions. \\
\end{tabular}

\subsubsection*{Voting}
\begin{tabular}{ll}
  \textbf{Customer} & Outsourcing for The Sandbox company limited. \\
  \textbf{Description} & Real-time voting for gameshow. \\
  \textbf{Team size} & 2 \\
  \textbf{My position} & Fullstack, lead \\
  \textbf{My responsibilities} & Development, deployment, maintenance, upgrade. \\
  \textbf{Technologies used} & MongoDB, ItoaJS, NextJS, PM2, Nginx, Chakra UI, \\ 
                             & Github actions. \\
\end{tabular}

\subsubsection*{Fan Portal}
\begin{tabular}{ll}
  \textbf{Customer} & Outsourcing for The Sandbox company limited. \\
  \textbf{Description} & Vote media and get giftcard. \\
  \textbf{Team size} & 3 \\
  \textbf{My position} & Fullstack, lead \\
  \textbf{My responsibilities} & Development, deployment, maintenance, upgrade. \\
  \textbf{Technologies used} & MongoDB, ItoaJS, ViteJS, PM2, Nginx, Chakra UI, \\
                             & Github actions. \\
\end{tabular}

\subsubsection*{Nhahang.so}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Ordering website for restaurant as a muti-tenant service. \\
  \textbf{Team size} & 3 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Maintenance, upgrade. \\
  \textbf{Technologies used} & PostgresSQL, Redis, RabbitMQ, NestJS, NextJS, \\
                             & PM2, Nginx, Cloudflare, Jenkin. \\
\end{tabular}

\subsubsection*{Bahana}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Food pickup place management. \\
  \textbf{Team size} & 3 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Maintenance, upgrade. \\
  \textbf{Technologies used} & PostgresSQL, Redis, RabbitMQ, NestJS, NextJS, \\
                             & PM2, Nginx, Cloudflare, Jenkin. \\
\end{tabular}

\subsubsection*{Cabinfood}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Food information management. \\
  \textbf{Team size} & 3 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Maintenance, upgrade. \\
  \textbf{Technologies used} & PostgresSQL, Redis, RabbitMQ, NestJS, NextJS, PM2, \\
                             & Nginx, Cloudflare, Jenkin. \\
\end{tabular}

\subsubsection*{CabinID}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Account management. \\
  \textbf{Team size} & 2 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Maintenance, upgrade. \\
  \textbf{Technologies used} & PostgresSQL, Redis, RabbitMQ, NestJS, NextJS, \\
                             & PM2, Nginx, Cloudflare, Jenkin. \\
\end{tabular}

\subsubsection*{Tiki App e-commerce}
\begin{tabular}{ll}
  \textbf{Customer} & Production \\
  \textbf{Description} & Mini app base on Tini Platform (raumamix, cafeongbau).  \\
  \textbf{Team size} & 3 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Maintenance, upgrade. \\
  \textbf{Technologies used} & PostgresSQL, Redis, RabbitMQ, NestJS, AngularJS, \\
                             & PM2, Nginx, Cloudflare, Jenkin. \\
\end{tabular}

\subsection*{  02/2022 - 04/2022: Break from work}
To rest after a traffic accident and focus on developing my graduation project.

\pagebreak

\subsection*{08/2021 - 02/2022: Full-stack developer at Sun Asterisk, Da Nang.}

\subsubsection*{DISCO (See https://careerforum.net)}
\begin{tabular}{ll}
  \textbf{Customer} & Japanese \\
  \textbf{Description} & Global recruitment, career support and educational marketing. \\
  \textbf{Team size} & 20 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Investigate, fix and report software bugs. \\
                               &  Expand database, implement business logic and user interface. \\
                               &  Software quality assurance as unit testing, interface testing. \\
  \textbf{Technologies used} & Ruby on rails, CSS, ERB, Angular, Jquery, \\
                             & Elastic Search, Redis, SQL, Nginx. \\
\end{tabular}



\subsection*{since 04/2019: Full-stack developer for freelancers.}
Working for small and medium-sized enterprises such as system development, upgrading, and maintenance. (2 years)


\subsubsection*{More than 10 projects}
\begin{sloppypar}
Build from scratch: doyoumined.com, thecupidroom.com, mayberoom.vn, japan-apple.jp, yensaodatquang.vn,
tuvilogic.com, hypesneaker.vn, b21shoemaker.store, shopwheydanang.com, madeuniform.vn,
luangiaituvi.net, review.vote, moneymaker.vn, mine-ea.com,...
\end{sloppypar}

\begin{tabular}{ll}
  \textbf{Customer} & Japanese, Australia, Vietnamese \\
  \textbf{Description} & Multi-tenant ecommerce, landing page, booking, blog, Saas,... \\
  \textbf{Team size} & 1-3 \\
  \textbf{My position} & Fullstack \\
  \textbf{My responsibilities} & Training, support and resolve problem for member. \\
                               &  Expand database, implement business logic and user interface. \\
                               &  Software quality assurance as unit testing, interface testing. \\
  \textbf{Technologies used} & Node.js, Mongodb, GraphQL, React.js, NextJS, devOps. \\
\end{tabular}


\pagebreak

\section{Education}
\textbf{Software Engineering} \\
\emph{Da Nang University of Science and Technology} \\
\textbf{Graduation:} 2022
\\
Here are some of the projects:
\begin{enumerate}
  \item Semester 1/2018-2019 - PBL\footnote{Project based learning}: Notification system for school \emph{(leader)}. Written in node.js, mongodb, heroku. Facebook API integration. Advisor by PhD Le Thi My Hanh.
  \item Semester 1/2019-2020 - PBL: Restaurant management system \emph{(leader)}. Written in C++ Console, MySQL. Advisor by PhD Dang Hoai Phuong.
  \item Semester 2/2019-2020 - PBL: Practical laboratory management system \emph{(leader)}. Written in C Sharp Winform, MySQL. Mentor by Enclave Company.
  \item Semester 1/2020-2021 - PBL: Lamport timestamp algorithm \emph{(leader)}. Written in Java. Advisor by MCS. Mai Van Ha.
  \item Semester 2/2020-2021 - PBL: Timekeeping using facial recognition \emph{(leader)}. Written in node.js, python, mongodb, react native. Microservices architecture. Deployment to Virtual Private Server. Advisor by PhD Bui Thi Thanh Thanh.
  \item Semester 1/2021-2022 - PBL: Social network service \emph{(leader)}. Written in node.js, mongodb, react native. Microservices architecture. Deployment to Virtual Private Server. Deployment to Virtual Private Server. Advisor by PhD Nguyen Van Hieu.
  \item Semester 2/2021-2022 - Thesis: System for creating and linking e-commerce. Microservices architecture. Deployment to Virtual Private Server. Advisor by PhD Le Thi My Hanh.
\end{enumerate}
Some exercises:
\begin{enumerate}
  \item Website programming \emph{(PHP)}.
  \item Digital signal processing \emph{(Matlab)}.
  \item Data science, Algorithm \emph{(Python)}.
\end{enumerate}	



\section{Technical Skills}
\subsection{Proficiency Description}
\paragraph{Basic knowledge} BK Basic knowledge, needs much guidance and support in using
the competence
\paragraph{Limited experience} LE Able to work in the area, needs some guidance in using the
competence
\paragraph{Practical application} PA Good knowledge and skills, works independently, has
sound experience in using the competence
\paragraph{Applied theory} AT Advanced knowledge and skills, provides guidance and direction
to others
\paragraph{Recognized authority} RA Exceptional knowledge and skills, perceived as an
authority in this competency area, is innovative in using the competence

\vspace{1em}
\begin{center}
  \begin{tabular}{| l | p{0.4\textwidth} |}
    \hline
    Skill & Proficiency\\
    \hline
    Data Construction & Basic knowledge \\
    Algorithm & Limited experience \\
    Programming Techniques & Practical application \\
    Object oriented programming & Applied theory \\
    Unified Modeling Language & Limited experience \\
    Computer network & Basic knowledge \\
    Database management system & Basic knowledge \\
    \hline
    MVC architectural pattern & Limited experience \\
    Git version control & Limited experience \\
    REST,
    GraphQL & Limited experience \\
    \hline
    React.js, Next.js & Practical application \\
    HTML, CSS & Limited experience \\
    Linux, Nginx, Github actions & Limited experience \\
    \hline
    Photoshop, Illustrator, Figma & Basic knowledge \\
    \hline

  \end{tabular}	
\end{center}

\section{My frameworks}
itoa.js - The power headless content management, custom from keystone.js. See more in https://www.npmjs.com/$\sim$truongduchuy910.
\begin{itemize}
  \item \textbf{@itoa/fields} ItoaJS Field Types including Text, Password, DateTime, Integer, and more.
  \item \textbf{@itoa/app-admin-ui} ItoaJS Admin UI App.
  \item \textbf{@itoa/access-control} ItoaJS Access Control parsing and validating utilities.
  \item \textbf{@itoa/adapter-mongoose} ItoaJS Mongoose Database adapter.
  \item \textbf{@itoa/app-graphql} ItoaJS GraphQL App.
  \item \textbf{@itoa/app-graphql-playground} ItoaJS GraphQL Playground App.
  \item \textbf{@itoa/server-side-graphql-client} A library for running server-side graphQL queries and mutations in Itoa.
  \item \textbf{@itoa/session} Tools to assist with setting up session management in your Itoa system.
  \item \textbf{@itoa/utils} Common utility functions used throughout @itoa packages.
  \item \textbf{@itoa/auth-password} Provides a basic password authentication strategy.
  \item \textbf{@itoa/file-adapters} Adapters for handling storage of the File type
  \item \textbf{@itoa/list-plugins} List level plugins which can update list config during list initialization including adding additional fields.
  \item \textbf{@itoa/itoa} The main @itoa class \& CLI. This is where the magic happens.
\end{itemize}
\end{document}
